Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-04 msre.tex
Flowchart & u233 temp coef
Fix equation and typo

I also calculated the normalized channel fission rate distribution by integrating the fission rate
within each fuel salt channel and normalizing the values such that the integrated fission rate in
each channel averages to 1 as follows
%
\begin{align}
  \text{Normalized fission rate of channel }i &= \frac{\text{Fission rate in channel }i}{
  \text{Total fission rate}}\cdot\frac{\text{Total number of channels}}{
    \text{Total fission rate in channels}} \nonumber \\
                                              &= \frac{\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}
  \phi_g(\vec{r})}{\sum^G_{g=1}\int_V\Sigma_{f,g}\phi_g(\vec{r})}\cdot\frac{N_i}{
  \sum^{N_i}_{i=1}\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}\phi_g(\vec{r})}.
\end{align}
%
The total fission rate includes fission rate contributions from peripheral fuel salt regions.
Division by total fission rate normalizes the fission rates across the different neutronics
methods.
Figures \ref{fig:1/4-no-rod} and \ref{fig:1/4-rod} show the normalized fission rate distributions
of the quarter-core model for the ``No Rod'' and ``Rod'' cases, respectively. I presented 1/8th
slices of the core in the figures because the distributions are symmetrical about the $y=x$ line
outside of statistical variances for OpenMC-CE. I combined the midpoints between the centroids of
neighboring fuel salt channels to form the diamond lattices shown in the figures.
Each diamond element in the figures corresponds a horizontally or vertically oriented channel
depicted in Figure \ref{fig:1/4-geom}. The lattice also provides a guide for subdividing the
annular fuel regions around the control rod thimbles. The fission rate
distributions omit four channels along the outer edge due to the proximity to peripheral annular
fuel regions and the consequent difficulty in accurately tallying fission rates.

@@

\subsubsection{Temperature Reactivity Coefficient}

>>>>

I also calculated the normalized channel fission rate distribution by integrating the fission rate
within each fuel salt channel and normalizing the values such that the integrated fission rate in
each channel averages to 1 as follows
%
\begin{align}
%  \text{Normalized fission rate of channel }i &= \frac{\text{Fission rate in channel }i}{
%  \text{Total fission rate}}\cdot\frac{\text{Total number of channels}}{
%    \text{Total fission rate in channels}} \nonumber \\
%                                              &= \frac{\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}
%  \phi_g(\vec{r})}{\sum^G_{g=1}\int_V\Sigma_{f,g}\phi_g(\vec{r})}\cdot\frac{N_i}{
%  \sum^{N_i}_{i=1}\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}\phi_g(\vec{r})}.
  \text{Normalized fission rate of channel }i &= \frac{(\text{Total number of channels})\times
    (\text{Fission rate in channel }i)}{\text{Total fission rate in channels}} \nonumber \\
                                              &= \frac{N_i\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}
  \phi_g(\vec{r}) dV}{
  \sum^{N_i}_{i=1}\sum^G_{g=1}\int_{V_i}\Sigma_{f,g}\phi_g(\vec{r}) dV}.
\end{align}
%
The total fission rate includes fission rate contributions from peripheral fuel salt regions.
Division by total fission rate normalizes the fission rates across the different neutronics
methods.
Figures \ref{fig:1/4-no-rod} and \ref{fig:1/4-rod} show the normalized fission rate distributions
of the quarter-core model for the ``No Rod'' and ``Rod'' cases, respectively. The figures present
1/8th slices of the core because the distributions are symmetrical about the $y=x$ line
outside of statistical variances for OpenMC-CE. I combined the midpoints between the centroids of
neighboring fuel salt channels to form the diamond lattices shown in the figures.
Each diamond element in the figures corresponds a horizontally or vertically oriented channel
depicted in Figure \ref{fig:1/4-geom}. The lattice also provides a guide for subdividing the
annular fuel regions around the control rod thimbles. The fission rate
distributions omit four channels along the outer edge due to the proximity to peripheral annular
fuel regions and the consequent difficulty in accurately tallying fission rates.

@@

\subsubsection{Temperature Reactivity Coefficient} \label{sec:temp-coef}
